Theory about Normal Basis on $F(2^k)$

### 2016-12-11 dissertation/prev.tex
dissertation v3:milestone

\subsection{Canonical Decision Diagrams}
The decision diagrams (DDs) are invented by inspirations of 
using optimized data structures to accelerate formal verification.
The most fundamental DD is the Binary DD (BDD), which originates from the 
Shannon's expansion:
\begin{equation}
f(x, y, \dots) = x f_x + x' f_{x'}
\end{equation}
where $f_x = f(x = 1)$ and $f_{x'} = f(x = 0)$ denote the positive and
negative co-factors of $f$ w.r.t. $x$, respectively.
A BDD is usually represented as a binary tree.
Its ordered and reduced form -- the Reduced Ordered Binary Decision Diagram (ROBBD)
\cite{BRYA86}, was the first significant contribution because of its canonicity.  
 ROBDDs represent a Boolean function as an
implicit set of points on a canonical directed acyclic graph
(DAG). Manipulation of Boolean functions can then be carried out as
composition operations on their respective DAGs.

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/BDD.pdf}
}
\caption{ROBDD representing Boolean function $\neg a \land b \land (c\lor d)$ with order $a>b>c>d$}
\label{fig:BDD}
\end{figure}

@@

\section{Word-level Techniques applied to Sequential Circuit Synthesis and Validation}
To better verify word-level designs, word-level verification techniques have been 
explored in recent years. Directly translating bit-vector problems to bit-level 
problems is called {\it bit-blasting}, and usually brings high redundancy and computational complexity in verification.
Attempts to develop pure word-level techniques can be found in
the rich domain of 
theorem proving \cite{arditi:bmd} and bit-vector SMT-solvers
\cite{boolector,cvc3,z3,bitvector98}, automated
decision procedures for Presburger arithmetic \cite{presburger,bultan:mixed_verification}, 
algebraic manipulation techniques 
\cite{devadas:algebraic_manipulation_iccd91}, or the ones based on
term re-writing \cite{AST}, etc.

Polynomial, integer and other non-linear representations have also
been researched: Difference Decision Diagrams (DDDs) \cite{ddd-csl99,ddd-mt-98}, interval
diagrams \cite{interval_dd}, interval analysis using polynomials
\cite{polynomial_sanchez99}, etc. Most of these have found 
application in constraint satisfaction for simulation-based
validation:  \cite{Ritter99,hsat,lpsat,brinkmann:asp-dac,Huang:tcad01,bitvector98}. Among
these, \cite{brinkmann:asp-dac,Huang:tcad01,bitvector98}
have been used to {\it solve} integer modular arithmetic on linear
expressions -- a different application from {\it representing}
finite field modulo-arithmetic on polynomials in a canonical form.

@@

The paper 
\cite{pruss:dac14} performs verification by deriving a canonical
word-level polynomial representation $\F$ from the circuit $C$. Their
approach views any arbitrary Boolean function (circuit) $f: \B^k
\rightarrow \B^k$ as a polynomial function $f: \Fkk \rightarrow \Fkk$,
and derives a canonical polynomial representation $\F$ over
$\Fkk$. They show that this can be achieved by computing a reduced 
\Grobner basis w.r.t. an {\it abstraction term order} derived from the
circuit. Subsequently, they propose a \underline{r}efinement of this
\underline{a}bstraction \underline{t}erm \underline{o}rder (called
RATO), that enables to compute the \Grobner basis of a smaller subset
of polynomials. The authors show that their approach can prove
correctness of up to 571-bit combinational GF multipliers.

@@

The use of algebraic geometry
for sequential circuit verification and symbolic model checking has
been presented before. Avrunin presented the
concept of symbolic MC using algebraic geometry in
\cite{Avrunin:CAV}. Later, in \cite{vardi-iasted07}, Vardi presented
GB-algorithms for CTL, LTL and 
bounded MC over Boolean rings. However, these approaches are a
straight-forward transformation of the problem to {\it bit-level}
Boolean GB engines which are used in lieu of BDDs or SAT solvers. All
the concepts of word-level reachability, abstraction-refinement using
interpolation or UNSAT cores, etc., that we desire was not the focus of
\cite{Avrunin:CAV,vardi-iasted07}.

>>>>

\subsection{Canonical Decision Diagrams}
The decision diagrams (DDs) are invented by inspirations of 
using optimized data structures to accelerate formal verification.
The most fundamental DD is the Binary DD (BDD), which originates from the 
Shannon's expansion:
\begin{equation}
f(x, y, \dots) = x f_x + x' f_{x'}
\end{equation}
where $f_x = f(x = 1)$ and $f_{x'} = f(x = 0)$ denote the positive and
negative co-factors of $f$ {\it w.r.t.} $x$, respectively.
A BDD is usually represented as a binary tree.
Its ordered and reduced form -- the Reduced Ordered Binary Decision Diagram (ROBBD)
\cite{BRYA86}, was the first significant contribution because of its canonicity.  
 ROBDDs represent a Boolean function as an
implicit set of points on a canonical directed acyclic graph
(DAG). Manipulation of Boolean functions can then be carried out as
composition operations on their respective DAGs.

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.45\textwidth]{newfig/BDD.pdf}
}
\caption{ROBDD representing Boolean function $\neg a \land b \land (c\lor d)$ with order $a>b>c>d$}
\label{fig:BDD}
\end{figure}

@@

\section{Word-level Techniques applied to Sequential Circuit Synthesis and Validation}
To better verify word-level designs, word-level verification techniques have been 
explored in recent years. Directly translating bit-vector problems to bit-level 
problems is called {\it bit-blasting}, and usually brings high redundancy and computational complexity in verification.
Attempts to develop pure word-level techniques can be found in
the rich domain of 
theorem proving \cite{arditi:bmd} and bit-vector SMT-solvers
\cite{boolector,cvc3,z3,bitvector98}, automated
decision procedures for Presburger arithmetic \cite{presburger,bultan:mixed_verification}, 
algebraic manipulation techniques 
\cite{devadas:algebraic_manipulation_iccd91}, or the ones based on
term re-writing \cite{AST}, {\it etc.}

Polynomial, integer and other non-linear representations have also
been researched: Difference Decision Diagrams (DDDs) \cite{ddd-csl99,ddd-mt-98}, interval
diagrams \cite{interval_dd}, interval analysis using polynomials
\cite{polynomial_sanchez99}, {\it etc.} Most of these have found 
application in constraint satisfaction for simulation-based
validation:  \cite{Ritter99,hsat,lpsat,brinkmann:asp-dac,Huang:tcad01,bitvector98}. Among
these, \cite{brinkmann:asp-dac,Huang:tcad01,bitvector98}
have been used to {\it solve} integer modular arithmetic on linear
expressions -- a different application from {\it representing}
finite field modulo-arithmetic on polynomials in a canonical form.

@@

The paper 
\cite{pruss:dac14} performs verification by deriving a canonical
word-level polynomial representation $\F$ from the circuit $C$. Their
approach views any arbitrary Boolean function (circuit) $f: \B^k
\rightarrow \B^k$ as a polynomial function $f: \Fkk \rightarrow \Fkk$,
and derives a canonical polynomial representation $\F$ over
$\Fkk$. They show that this can be achieved by computing a reduced 
\Grobner basis {\it w.r.t.} an {\it abstraction term order} derived from the
circuit. Subsequently, they propose a \underline{r}efinement of this
\underline{a}bstraction \underline{t}erm \underline{o}rder (called
RATO), that enables to compute the \Grobner basis of a smaller subset
of polynomials. The authors show that their approach can prove
correctness of up to 571-bit combinational GF multipliers.

@@

The use of algebraic geometry
for sequential circuit verification and symbolic model checking has
been presented before. Avrunin presented the
concept of symbolic MC using algebraic geometry in
\cite{Avrunin:CAV}. Later, in \cite{vardi-iasted07}, Vardi presented
GB-algorithms for CTL, LTL and 
bounded MC over Boolean rings. However, these approaches are a
straight-forward transformation of the problem to {\it bit-level}
Boolean GB engines which are used in lieu of BDDs or SAT solvers. All
the concepts of word-level reachability, abstraction-refinement using
interpolation or UNSAT cores, {\it etc.}, that we desire was not the focus of
\cite{Avrunin:CAV,vardi-iasted07}.
